Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-29 ms.qmd
landscape. Trying this out

\end{landscape}

```{r}
#| label: fig-fig3
#| fig-cap: Predicted mean acclimation and acute "$lnRR_{Q_{10}}$" for adult and juevenile life-history stages for A) Marine, B) Freshwater and C) Terrestrial ectotherms.

>>>>

\end{landscape}
\newpage
```{r}
#| label: fig-fig3
#| fig-cap: Predicted mean acclimation and acute "$lnRR_{Q_{10}}$" for adult and juevenile life-history stages for A) Marine, B) Freshwater and C) Terrestrial ectotherms.
